---
title: "Distributions homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

# MVP

##Question 1.**  
Load the data, `clean_names()` and explore it.
```{r}
library(tidyverse)
library(janitor)
library(skimr)
```
```{r}
items <- read_csv("data/20190928-items.csv") %>% 
  clean_names() 
```




```{r}
items %>% 
  summarise(across(.fns = ~sum(is.na(.x))))
```



##Question 2.**  
Find the brand with the highest numbers of phones in the dataset.
```{r}
items %>% 
  group_by(brand) %>% 
  summarise(nr_phones = n()) %>% 
  slice_max(nr_phones, n = 1)
```


##Question 3.**  
For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?
```{r}
samsung_stats <- items %>%
  filter(brand == "Samsung") %>%
  summarise(
    number = n(),
    mean = mean(rating),
    sd = sd(rating)
  )
```

```{r}
items %>% 
  filter(brand == "Samsung") %>%
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), fill = "#E69F00", col = "black", bins = 25) +
  theme_bw() +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = samsung_stats$mean, 
      sd   = samsung_stats$sd
    ),
    col = "red",
    size = 1
  )
```
Continuous uniform distribution would be a good option. We have the boundary of rating defined, between 1 to 5, and within this range we can have any continuous value.



##Question 4.**  
We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the `mean()` and `sd()` of your distribution in an earlier question. Use these values to calculate the *proportions* of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution. 
```{r, eval=FALSE}
items %>% 
  filter(brand == "Samsung") %>% 
  filter(rating >= samsung_stats$mean - samsung_stats$sd) %>%
  filter(rating <= samsung_stats$mean + samsung_stats$sd) %>%
  summarise(prop_within_1sd = n() / samsung_stats$number)
```
The proportion within the sd1 it is 79,3% that represent a value higher
than should be expected (68%). This means that 79% of ratings for samsung are 
between 2.888514 (mean-sd1) and 4.258086 (mean+sd1).

```{r}
items %>% 
  filter(brand == "Samsung") %>% 
  filter(rating >= samsung_stats$mean - samsung_stats$sd*2) %>%
  filter(rating <= samsung_stats$mean + samsung_stats$sd*2) %>%
  summarise(prop_within_2sd = n() / samsung_stats$number)
```
The proportion expected within sd2 would be 95%, however by samsung rating the 
proportion of ratings within sd2 was 91,94%. It means 
that 91,94% o values are within 2.203728 (mean-sd2 = 3.5733 + 0.6847859 *2)
and 4.942872(mean+sd2 = 3.5733 + 0.6847859 *2).

```{r}
items %>% 
  filter(brand == "Samsung") %>% 
  filter(rating >= samsung_stats$mean - samsung_stats$sd*3) %>%
  filter(rating <= samsung_stats$mean + samsung_stats$sd*3) %>%
  summarise(prop_within_3sd = n() / samsung_stats$number)
```
97,98% of ratings of Samsung are within 1.518942 and 5. The proportion expected 
between mean-sd3 and mean+sd3 should be 99,7%.


