---
title: "R Notebook"
output: html_notebook
---

#Libraries
```{r}
library(tidyverse)
library(janitor)
```

#Load Data
```{r}
books <- read_csv("2_weekend_homework/data/books.csv")
head(books)
```

#First contact with dataset
```{r}
view(books)       #investigate the variables/columns

sum(is.na(books)) #Get total number of missing values

summary(books)
```

```{r}
books %>% 
   summarise(across(.fns = ~ length(.x))) #number of observations/variable.
```


#Edit names
```{r}
books_renamed <- books_janitor_clean %>% 
  rename("row_id"    = "rowid",
         "isbn_13"  = "isbn13")

names(books_renamed)
```
#Check nonconformities in variables
```{r}
# with summary() function it was possible to see that are books with a number 
# of pages equal to zero what is not supposed.

#Counting how many observations there are per number of pages. 
books_renamed %>% 
  group_by(num_pages) %>% 
  summarise(grp_count = sum(n())) %>% 
  slice_min(num_pages, n = 5)
```

Try to find some relations between number of pages and raking
```{r}
range_ratings <- books_renamed %>% 
  filter(num_pages == 0) %>% 
  summarise (range(ratings_count)) %>% 
  pull()

range_ratings


#Comment:
# Any relation looking for ratings_counts was find out for number of pages be equal 0. 
# The range o values do not give us any conclusion.
```
```{r}
#isbn_13 should have 13 digits and isbn 10 digits.
#Here we verify if there are observations where the variable isbn13 as less than 13 digits and isbn with less than 10.
library(stringr)
books_renamed %>% 
   summarise(count_isbn_13_less_13 = sum(str_length(isbn_13) == 13),
             count_isbn_less_10    = sum(str_length(isbn)    == 10))
```

```{r}
#The observation where the variable isbn is different of 10 digit, was deleted
books_isbn <- books_renamed %>% 
  filter(str_length(isbn) == 10)

nrow(books_renamed) - nrow(books_isbn)
dim(books_isbn)

#As expected 1 row was deleted
```
#Missing Values
```{r}
sum(is.na(books)) #get the numbers of missing values (NA and NaN)

books %>% 
  summarise(across(.fns = ~ sum(is.na(.x))))

#Comment: There is not missing values in all dataset
```

```{r}
#Impute NA for all observations with number of pages equal to 0
books_na <- books_isbn %>%
  mutate(num_pages = na_if(num_pages, 0))
```

```{r}
#As expected the number o NA is 76
books_na %>% 
  summarise(count = sum(is.na(num_pages))) %>% 
  pull()
```

```{r}
#Remove all NA
books_final <- books_na %>% 
  drop_na()


nrow(books_na) - nrow(books_final)
#Number of NA removed was 76 as expected. This values is the same of books with zero pages that there were in the begin
```
1. What five books have the highest `average_rating` ?
```{r}
books_renamed %>%
  summarise(title, average_rating) %>% 
  arrange(desc(average_rating)) %>% 
  head(5)
```

2. Which book has the most `text_reviews` ?
```{r}
#The book with most text_reviews is the Twilight (Twilight #1) with 3.59.
books_renamed %>%
  arrange(text_reviews_count) %>% 
  tail(1)
```

```{r}
# Other way to answer 'Which book has the most `text_reviews` ?'
books_renamed %>%
  slice_max(text_reviews_count, n = 1)
```

3. Which book has the most ratings?
```{r}
#The book with the most rating is the Twilight (Twilight #1) with 4597666.
books_renamed %>%
  slice_max(ratings_count, n = 1)
```

4. Which publisher has the highest `average_rating`?
```{r}
#There are 22 publishers with the highest same average rating.
books_renamed %>% 
  slice_max(average_rating, n = 1) 
```

5. How many pages is the longest book for each `language_code`?
```{r}
#The book with more pages is the The Complete Aubrey/Maturin Novels (5 Volumes)
#with 6576 pages.
books_renamed %>% 
  slice_max(num_pages, n = 1) 
```

6. What is the highest rated book for each `language_code`?
```{r}
books_renamed %>% 
  select(language_code, ratings_count, title) %>% 
  group_by(language_code) %>% 
  summarise(high_rate = max(ratings_count))
```

