---
title: "R Notebook"
output: html_notebook
---


#Initialize ----
```{r}
library(tidyverse)
```


#Question 1 ----
```{r}
library(CodeClanData)
df <- drinks_content
head(df)
```
```{r}
#An overall picture of dataset - Using glimpse() we can see the dimension of our dataset (dim()) the variable names (names()) and the variables types
glimpse (df)
```

#Question 2 ----
```{r}
#Create a sub dataset just with the variables we need
df_selected_var <- select(df,Beverage_category, Beverage, Beverage_prep,Calories)
```

```{r}
#If there is any NA will be deleted
drop_na(df_selected_var)
```

#Question 3 ----
```{r}
#Create a new variable called calorie_diff 
df_calorie_diff <- mutate(df_selected_var, calories_diff = Calories-135)
df_calorie_diff
```
```{r}
df_sugar_cubes <- mutate(df_calorie_diff, sugar_cubes_above_10 = calories_diff / 10 > 0)
df_sugar_cubes
```

#Question 4 ----
```{r}
grp_category <- group_by(df_calorie_diff, Beverage_category)
summarised_category <- summarise(grp_category, mean_calories_category = mean(Calories))
summarised_category
```

```{r}
arrange(summarised_category, desc(mean_calories_category))
```
  The mean of calories by beverage category was sorted by descendent order, and this way we could find and conclued which categorie are most and the less calorified, there are:
  - Top 3 with most calories (from higher to lower): Smoothies (282.22 cal.), Frappuccino Blended Coffee        (276.95 cal.) and Signature Espresso Drinks (250.00 cal.);
  - The last 3 with less calories (from higher to lower): Classic Espresso Drinks (140.17 cal.), Shaken Iced     Beverages (114.44 cal.) and at the end we find the Coffee (4.25 cal.).

#Question 5 ----
```{r}
grp_pre <- group_by(df_calorie_diff,Beverage_prep) 
summarised_prep <- summarise(grp_pre, mean_calories_pre = mean(Calories))
summarised_prep
```

#Question 6 ----
```{r}
mean_prep <- mean(pull(summarised_prep, mean_calories_pre))
mean_prep
```
```{r}
mutate(summarised_prep, calories_above_mean = mean_calories_pre > mean_prep)
```

#Question 7 ----
```{r}
grp_drink <- group_by(df_calorie_diff, Beverage, Beverage_category, Beverage_prep)
summarised_drink <- summarise(grp_drink, drink_cal = sum(Calories))
summarised_drink
```
```{r}
arrange(summarised_drink, desc(drink_cal))
```

