---
title: "Homework - features and elements of multiple regression"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

# MVP

```{r}
library(tidyverse)
library(janitor)
```


1. Load the `housing_prices.csv` data set and undertake an initial exploration of the data. You will find details on the data set on the relevant [Kaggle page](https://www.kaggle.com/camnugent/california-housing-prices)
```{r}
house_prices <- read_csv("data/housing_prices.csv") %>% 
  clean_names()

head(house_prices)
```



2. We expect the `total_rooms` of houses to be strongly correlated with `total_bedrooms`. Use `ggpairs()` to investigate correlations between these two variables.
```{r}
library(GGally)

house_prices %>% 
  select(total_rooms, total_bedrooms) %>% 
  ggpairs()

# There is a very strong positive correlation between the total of rooms and total of beds
```


3. So, we do find significant correlations. Let's drop `total_bedrooms` from the dataset, and use only `total_rooms` going forward.

```{r}
house_prices_rm_total_bedrooms <- house_prices %>% 
  select(-total_bedrooms)

head(house_prices_rm_total_bedrooms)
```


4. We are interested in developing a regression model for the `median_house_value` of a house in terms of the possible predictor variables in the dataset.

  i. Use `ggpairs()` to investigate correlations between `median_house_value` and the predictors (this may take a while to run, don't worry, make coffee or something).
```{r}
house_prices_rm_total_bedrooms %>% 
  ggpairs()

# Just consider as a correlaction relevant between the median_house_value and median_income. There is a positive strong correlaction between both variables.

# The correlation between median_house_value and the other variables are very week.
```
  

  ii. Perform further `ggplot` visualisations of any significant correlations you find.
```{r}
house_prices_rm_total_bedrooms %>% 
  # select(median_house_value, median_income) %>% 
  ggplot() +
  aes(y = median_house_value, x = median_income) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```


5. Shortly we may try a regression model to fit the categorical predictor `ocean_proximity`. Investigate the level of `ocean_proximity` predictors. How many dummy variables do you expect to get from it?
```{r}
house_prices_rm_total_bedrooms %>% 
  count(ocean_proximity)

house_prices_rm_total_bedrooms %>% 
  distinct(ocean_proximity)

# It is expected to get 4 dummy variables from 
```

 
6. Start with simple linear regression. Regress `median_house_value` on `median_income` and check the regression diagnostics.
```{r}
library(mosaic)

lm <- lm(formula = median_house_value ~ median_income,
         data    = house_prices_rm_total_bedrooms)

summary(lm)

autoplot(lm)

# The diagnostic plot seems reasonable..
# The Residuals vs Fitted plot seems good having the values without variation and across zero, some deviation from normality in the high and lower quantile residuals in the Normal Q-Q plot, and good heteroscedasticity in the Scale-Location plot.

# The relationship is statistically significant, as the p-value is less than a typical significance level of 0.05.
```
 

7. Add another predictor of your choice. Check your assumptions, diagnostics, and interpret the model.
```{r}
lm1 <- lm(formula = median_house_value ~ median_income + population,
          data    = house_prices_rm_total_bedrooms)

summary(lm1)

autoplot(lm1)

#Residuals vs Fitted and Scale-Location are ok, while Normal Q-Q in the higher and the lower residuals are a relative deviation.
#p-value is significante to median_income, but it is not to population (significance level lower than 0.05)
```

```{r}
coplot(formula = median_house_value ~ median_income | population, 
       data    = house_prices_rm_total_bedrooms)
```

