---
title: "Simple linear regression homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

```{r}
library(tidyverse)
library(janitor)
library(broom)
library(ggfortify)
```


The file `project_management.csv` contains data sampled from the recent work schedule of a small construction company. Column `estimated_length` contains the estimated length of a building job in days, while column `actual_length` contains the actual recorded length of the job in days. 

We are interested in determining the accuracy of the job estimations made by the company using simple linear regression, so we will eventually want to run a **simple linear regression** using `actual_length` as the dependent variable, and `estimated_length` as the independent variable.


* Load the data into a dataframe `project`
```{r}
project_management <- read_csv("data/project_management.csv") %>% 
  clean_names()

head(project_management)
```

* Plot the data, taking `estimated_length` as the independent variable and `actual_length` as the dependent variable. 
```{r}
project_management %>% 
  ggplot(aes(x = actual_length, y = estimated_length)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```



* Calculate the correlation coefficient of `estimated_length` and `actual_length` and interpret the value you obtain.
```{r}
project_management %>% 
  summarise(r = cor(estimated_length, actual_length))

#ANSWER:
# There is a very strong positive correlation between estimated_length and actual_length.
```



* Perform a simple linear regression using `actual_length` as the dependent variable, and `estimated_length` as the independent variable. Save the model object to a variable.
```{r}
model <- lm(formula = actual_length ~ estimated_length, 
            data = project_management)

model
```


* Interpret the regression coefficient of `estimated_length` (i.e. slope, gradient) you obtain from the model. How do you interpret the $r^2$ value reported by the model?
```{r}
summary(model)

tidy_output <- clean_names(tidy(model))
tidy_output

glance_output <- clean_names(glance(model))
glance_output


#ANSWER:

#For one unit increase in independent variable (estimated_length) values changes the dependent variable by an amount equal to 1.2235 (slope).

#r_squared = 0.6474772, The proportion of the variation in the dependent variable that can be explained by variation in the independent variable, it means that the  64,75% of the variation in actual_length is explanined (is pedictable from) by variation in estimated_length.
```



* Is the relationship statistically significant? Remember, to assess this you need to check the $p$-value of the regression coefficient (or slope/gradient). But you should first check the regression diagnostic plots to see if the $p$-value will be reliable (don't worry about any outlier points you see in the diagnostic plots, we'll return to them in the extension).
```{r}
autoplot(model)
```
*Residuals vs Fitted*
Is expected a horizontal line across the zero, or in small data wobble around zero. We could say that this plot is fine.

*Norma Q-Q*
Residuals are well-described as normally distributed


*Scale-Location*
We would expect to see the line stay close to a constant or positive value (or wobble around a constant value if you have little data). We could say that this plot is fine.

We should trust the p-values of the coefficient in either of these regression fits: the conditions for the residuals have been satisfied, meaning the hypothesis tests are safe.
