---
title: "Text Mining Homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE, fig.align = "center", message = FALSE, warning = FALSE)
```

# MVP

Using the dataset `austen_books()` from the package `janeaustenr`:
```{r}
library(janeaustenr)
library(tidyverse)
library(tidytext)
```

1. Find the most common words in both Pride & Prejudice and Sense & Sensibility.
```{r}
prideprejudice_nostop_words <- tibble(
  id   = seq_along(prideprejudice),
  text = prideprejudice) %>% 
  unnest_tokens(word, text) %>% 
  anti_join(stop_words, by = "word") %>% 
  count(word, sort = TRUE)


sensesensibility_nostop_words <- tibble(
  id   = seq_along(sensesensibility),
  text = sensesensibility) %>% 
  unnest_tokens(word, text) %>% 
  anti_join(stop_words, by = "word")%>% 
  count(word, sort = TRUE)
```

```{r}
prideprejudice_nostop_words
sensesensibility_nostop_words
```


2. Find the most common words in both Pride & Prejudice and Sense & Sensibility, not including stop words.
```{r}
prideprejudice_stop_words <- tibble(
  id   = seq_along(prideprejudice),
  text = prideprejudice) %>% 
  unnest_tokens(word, text) %>% 
  count(word, sort = TRUE)


sensesensibility_stop_words <- tibble(
  id   = seq_along(sensesensibility),
  text = sensesensibility) %>% 
  unnest_tokens(word, text) %>% 
  count(word, sort = TRUE)
```

```{r}
prideprejudice_stop_words
sensesensibility_stop_words
```


3. Find the most common sentiment words in both Pride & Prejudice and Sense & Sensibility.
```{r}
prideprejudice_nostop_words_sentiments <- prideprejudice_nostop_words %>% 
  left_join(get_sentiments("nrc")) %>% 
  drop_na() %>% 
  group_by(sentiment) %>% 
  summarise(count_sentiment = n()) %>% 
  arrange(desc(count_sentiment))


sensesensibility_nostop_words_sentiments <- sensesensibility_nostop_words %>% 
  left_join(get_sentiments("nrc")) %>% 
  drop_na() %>% 
  group_by(sentiment) %>% 
  summarise(count_sentiment = n()) %>% 
  arrange(desc(count_sentiment))
```
```{r}
prideprejudice_nostop_words_sentiments
sensesensibility_nostop_words_sentiments
```


# Extension

Taking your results above. Can you create a plot which visualises the differences between the books?  
```{r}
titles <- c("Pride & Prejudice", 
            "Sense & Sensibility")
books <- list(prideprejudice,
              sensesensibility)

books <- books %>%
  purrr::map_chr(paste, collapse = " ")
str(books)

plot_sentiments <- tibble(
  title = titles,
  text = books
) %>%
  unnest_tokens(word, text) %>% 
  anti_join(stop_words, by = "word") %>% 
  left_join(get_sentiments("nrc")) %>% 
  drop_na() %>% 
  group_by(title, sentiment) %>% 
  summarise(count_sentiment = n()) %>% 
  ggplot(aes(x = sentiment, y = count_sentiment, fill = title)) +
  geom_col(position = "dodge") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  geom_text(aes(label = count_sentiment), 
            position = position_dodge(0.9), 
            vjust = -0.3, 
            size = 3) +
  labs(title = "Sentiments per book",
       x = NULL, 
       y = NULL)

plot_sentiments
```




