---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(janitor)
```

#---- MVP ----
#Question 1
```{r}
df <- read_csv("6_homework_cleaning_data/data/movies.csv")
head(df)
```

```{r}
glimpse(df)
```
- Think about if values that exist in some variables makes sense.
- Using functions like 'rename()' to change the name of variables to leave them more understandable.
- Turn the binary values (0,1) of a variable in a locical values (True/False) - 'col_logical()'
- Turn the values of variables more suggestives that do not leave any doubts about what they means
- Verify if there are some logical by missing values
- Take decisions about missing values, if grip them all using 'drop.na()' function or if we should impute values like the mean, median, mode for the NA using 'coalesce() function'

#Question 2
```{r}
movies_selected <- df %>% select(original_title, runtime, budget)
movies_selected
```

#Question 3
select per each variable the rows that have missing values
```{r}
movies_selected %>% filter(is.na(original_title))
movies_selected %>% filter(is.na(runtime))
movies_selected %>% filter(is.na(budget))
```
Count how many missing values we have per variable
```{r}
movies_selected %>% summarise(count_NAs_title = sum(is.na(original_title)))
movies_selected %>% summarise(count_NAs_runtime = sum(is.na(runtime)))
movies_selected %>% summarise(count_NAs_budget = sum(is.na(budget)))
```

#Question 4
```{r}
movies_runtime <- movies_selected %>%
  mutate(runtime = na_if(runtime, "0")) #A film with runtime=0 does not make sense. By na_if() function, all zero values in runtime will be assigned as NA

movies_runtime %>% filter(is.na(runtime)) #show the observations where the variable runtime has NA
movies_runtime %>% summarise(count_NAs_runtime = sum(is.na(runtime))) #count how many NAs exists
```

#Question 5
```{r}
#Replace with the median all NA in runtime's variable
movies_imputed <- movies_runtime %>%
  mutate(runtime = coalesce(runtime, median(runtime, na.rm = TRUE)))
```

```{r}
#Count how many NAs there are in runtime's variable
movies_imputed %>% filter(is.na(runtime))
```

#Question 6
```{r}
movies_imputed %>% slice_max(runtime, n=10)
movies_imputed %>% slice_min(runtime, n=10)
```

#Question 7
```{r}
movies_imputed <- movies_runtime %>%
  mutate(new_budget = if_else(
                               budget < 100,
                               mean(budget),
                               budget)
         )
movies_imputed
```

```{r}
movies_imputed %>% filter(budget < 100)
```


#---- Extention ----
#Question 1
```{r}
movie_budgets <- movies_imputed %>% 
  mutate(budget_type = case_when(budget < 12000000 ~ "Small budget",
                                 budget > 12000000 & budget < 40000000 ~ "Medium budget",
                                 budget > 40000000 ~ "Big budget"))
movie_budgets
```

#Question 2
```{r}
df_character <- df %>%
  #group_by(allegiances) %>%      
  summarize(across(
    where(is.character), na.rm = TRUE))
df_character
```

```{r}
df_numeric <- df %>%
  #group_by(allegiances) %>%      
  summarize(across(
    where(is.numeric), na.rm = TRUE))
df_numeric
```

