---
title: "Probability homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, messages = FALSE, fig.align = 'center')
```


# MVP

## The Titanic
```{r, message = FALSE}
library(prob)
library(gtools)
library(tidyverse)
```


```{r}
titanic <- read_csv("data/titanic.csv")
```

```{r}
class_values <- titanic %>% 
  distinct(class)
```


```{r}
#create a logical variable to distinguish passengers(FALSE) and crew members (TRUE)
titanic_class <- titanic %>% 
  mutate(crew_or_not =
          if_else(
            class %in% c("1st", "2nd", "3rd"), 
            FALSE,
            TRUE
          )) %>% 
  select(survived, crew_or_not)

titanic_class
```

```{r}
titanic_prob_table <- titanic_class %>%
  tabyl(survived, crew_or_not) %>%
  adorn_totals(where = c("row", "col")) %>%
  adorn_percentages(denominator = "all") %>%
  adorn_title()

titanic_prob_table
```
```{r}
#one resolution could be looking for the values of table. P(A AND B) / P(B)
survived_crew_table      <- 0.0956 / 0.4032
survived_passenger_table <- 0.226 / 0.5967
```


```{r}
#a second solution could be more manual
survived_crew <- titanic_class %>% 
  filter(crew_or_not == "TRUE") %>% 
  summarise(prob_crew = sum(survived == "yes") / n())

survived_passenger <- titanic_class %>% 
  filter(crew_or_not == "FALSE") %>% 
  summarise(prob_passenger = sum(survived == "yes") / n())

survived_crew 
survived_passenger
```



**MVP**  

**Question 1.**  
If I roll a six-sided dice once, what is the probability of getting a number less than 5?
```{r}
4/6
```


**Question 2.**  
How many outcomes are there in the sample space of an experiment in which we toss three dice?
```{r}
tosscoin(3)

#8 outcomes
```



**Question 3.**  
In an experiment where we roll four dice:

  * how many outcomes are in the event where the total of the four dice equals $5$, $6$ or $7$)?
```{r}
s_four_dice <- rolldie(4)

s_four_dice %>% 
  mutate(total = X1 + X2 + X3 + X4) %>% 
  filter(total %in% c(5, 6, 7))
```
  
  * what is the probability of this event?
```{r}
s_four_dice <- rolldie(4)
event_prob <- s_four_dice %>% 
  mutate(total = X1 + X2 + X3 + X4) %>% 
  filter(total %in% c(5, 6, 7)) %>% 
  nrow() / nrow(s_four_dice)
  
event_prob
```
  
  * what assumptions do we apply in answering part ii?
```{r}
#34 possible results in a total of 2207
```


**Question 4.**  
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?
```{r}
height <- c(170, 171, 172, 173, 174, 175)

height_table <- as_tibble(permutations(n = 5, r = 5,
                        v = height,
                        repeats.allowed = FALSE))

prob_order <- 1 / nrow(height_table) 
prob_order
```





<details>
<summary>**Hint**</summary>
This is an arrangement where order matters. Of all the possible arrangements, how many are correct?
</details>

<br>
**Question 5.**  
I roll six dice:

  * what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
  * what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?
  
<details>
<summary>**Hint**</summary>
Have a look at the `isin()` function in the `prob` package. For example, to `filter` all rows containing $6$, $1$, $2$ in that order, you could use `isin(., c(6, 1, 2), ordered = TRUE)`
</details>

<br>
**Question 6.**  
If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades? <br>

<details>
<summary>**Hints**</summary>

* Investigate the `cards()` function in the `prob` package, if you'd like to try this in R (make a deck without jokers). 
* You could think about adding your own `black_card` random variable to the sample space, which would be `TRUE` if the `suit` is 'Spade' or 'Club', and `FALSE` otherwise.
</details>

<br>

# Extension

Answer more than 4 consolidation questions