---
title: "Homework - CIs"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
library(fastGraph)
```


# MVP ----------------
## Task 1.**  
Load the data again, `clean_names()`, and re-familiarise yourself with it
```{r}
ames <- read_csv("data/ames.csv") %>% 
  clean_names()
```

```{r}
glimpse(ames)
```


## Task 2.**  
Investigate the distribution of `lot_area`. Is the distribution roughly normal? If not, what problems do you find?
```{r}
ames %>% 
  ggplot()+
  geom_histogram(aes(lot_area), bins = 40)
```

```{r}
qqnorm(ames$lot_area)
qqline(ames$lot_area)
```
```{r}
library(car)
qqPlot(ames$lot_area)
```
The distribution is not roughly normal. It looks like right Skewness.


## Task 3.**  
Compute and visualise a bootstrap sampling distribution for the `mean(lot_area)` of the sold houses.
```{r}
bootstrp_resample_lot_area <- ames %>% 
  rep_sample_n(size = 2930, replace = TRUE, reps = 5000) %>% 
  summarize(mean_lot_area   = mean(lot_area),
            stderr_lot_area = sd(lot_area))

bootstrp_resample_lot_area
```
```{r}
bootstrp_resample_lot_area %>%
  ggplot(aes(x = mean_lot_area)) +
  geom_histogram(col = "white", fill = "steel blue", alpha = 0.7)
```


## Task 4.**  
Use your bootstrap distribution to calculate a $95\%$ CI for `mean(lot_area)`, and visualise it on the distribution
```{r}
infer_resample <- ames %>%
  specify(response = lot_area) %>%
  generate(reps = 5000, type = "bootstrap") %>%
  calculate(stat = "mean")

infer_resample
```
```{r}
infer_ci_95 <- infer_resample %>%
  get_confidence_interval(level = 0.95, type = "percentile")
infer_ci_95

infer_resample %>%
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = infer_ci_95)
```


## Task 5.**  
You would like to know the `mean(lot_area)` of the sold houses with higher confidence. Calculate the $99\%$ CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the $95\%$ CI? Does that make sense?
```{r}
infer_ci_99 <- infer_resample %>%
  get_confidence_interval(level = 0.99, type = "percentile")
infer_ci_99


infer_resample %>%
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = infer_ci_99)
```
As the size of sample is the same, with the increase of CI by 99% there were a increase of width of CI. It is what were expected, for samples the same size the width of the CI increases as confidence level increases.


## Task 6.**  
Calculate the point estimate of the `mean(lot_area)`
```{r}
mean_infer <- infer_resample %>%
  summarise(mean = mean(stat))

mean_infer
```

# Extension ----------
## Task 1.**  
Calculate a point estimate and $95\%$ CI for the proportion of houses in the data built before 1920.  Does the number of `reps` you use matter? [Investigate `reps` from $200$ up to $50000$, memory of your laptop permitting].
```{r}
built_before_1920 <- ames %>% 
  select(year_built, lot_area) %>% 
  mutate(before_1920 = as.logical(year_built < 1920))


bootstrap_resample_before_1920_200 <- built_before_1920 %>%
  specify(response = before_1920, success = "TRUE") %>%
  generate(reps = 200, type = "bootstrap") %>%
  calculate(stat = "prop")

bootstrap_resample_before_1920_50000 <- built_before_1920 %>%
  specify(response = before_1920, success = "TRUE") %>%
  generate(reps = 50000, type = "bootstrap") %>%
  calculate(stat = "prop")

```

```{r}
before_1920_ci_95_200 <- bootstrap_resample_before_1920_200 %>%
  get_confidence_interval(level = 0.95, type = "percentile")
before_1920_ci_95_200

before_1920_ci_95_50000 <- bootstrap_resample_before_1920_50000 %>%
  get_confidence_interval(level = 0.95, type = "percentile")
before_1920_ci_95_50000


bootstrap_resample_before_1920_200 %>%
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = before_1920_ci_95_200)

bootstrap_resample_before_1920_50000 %>%
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = before_1920_ci_95_50000)

```

```{r}
bootstrap_resample_before_1920_200 %>%
  summarise(point_est = mean(stat))

bootstrap_resample_before_1920_50000 %>%
  summarise(point_est = mean(stat))
```
The number of `reps` matter. how much reps we use, will be generated an approximation of the sampling distribution from single sample.